Fisheries management when quotas are costly to change

### 2014-07-31 manuscripts/presentation.Rmd
layout adjusted

@@

<!--
## Postulate: policy intertia

> Policies are costly to change

## We're quite good at accounting for _ecological_ dynamics

<small> Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7) </small>

-->

>>>>

> ## As ecologists, we've ever focused on accounting for _ecological_ dynamics

Model setup
------------

- Focus on _stochastic_ dynamics: thus a constant harvest is not optimal.

- Follow the textbook classic approach: Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7)

Population grows under a Beverton-Holt stock-recruitment curve,

- subject to multiplicitive log-normal growth shocks $Z_t$

@@
